### 2024-08-20 paper.tex
redefine set of bs.  much better now

\section{Finding the irreducible components of \(U_0\)}
\subsection{Introduction}
Let \(X\) be nilpotent with Jordan basis \((e_{ij}')_{1 \leq i \leq k, 1 \leq j \leq \lambda_i'}\).
Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
Let
\[U_0 = \{(A_{0,b}, U) \in V\}.\]
We will find the irreducible components of \(U_0\).
\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
Then set \(q_i(b) = \lambda_i - p_i(b)\).
When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
\par For any \(I \subseteq \{1, ..., k\}\) and any map \((i \mapsto \rho_i) : I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\), define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(i \in I\), \(p_i = \rho_i\)
    \item For all \(i \notin I\), one of the following holds.
    \begin{itemize}
        \item \(q_i \geq n\)
        \item There is an \(i' \in I\) such that \(q_{i'} \leq q_i\) and \(p_{i'} \geq p_i\)
        \item \(p_i = 0\)
    \end{itemize}
\end{itemize}
Then let \(U_{I, (\rho_i)} = \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).

@@

\subsection{A study of \(B_{I, (\rho_i)}\)}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4).
Define \(\{i_1 < \cdots < i_r\} := I\).
For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).

\begin{lemma}\label{bs_fact}
    For any \(b \in B_{I, (\rho_i)}\) and any \(k \in \{0, ..., r\}\), we have \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
    \begin{itemize}
        \item 
    \end{itemize}
\end{lemma}
To see why this choice makes some sort of sense, look at the shape \(\mu\) of the Jordan basis of the previous subsection.
\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\), where
    \[B_{I, (\rho_i)}' := \{b \in \mathbb{C}^m : \forall i \in I. \; p_i \leq \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
    \[\textrm{ where } k = \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\}.\]
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    So, let \(i \notin I\), and let \(k = \min\{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).

>>>>

\section{Finding the irreducible components of \(U_0\)}
\subsection{Introduction}
Let \(X\) be nilpotent with Jordan basis \((e_{ij}')_{1 \leq i \leq k, 1 \leq j \leq \lambda_i'}\).
Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
Let
\[U_0 = \{(A_{0,b}, U) \in V\}.\]
We will find the irreducible components of \(U_0\).
\par We write \(b_{ij}\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}\).
For each row \(i\), let \(p_i(b) = \max\{j : b_{ij} \neq 0\}\) (the maximum of the empty set is zero).
Then set \(q_i(b) = \lambda_i - p_i(b)\).
When it is clear enough from context, we will just write \(p_i\) and \(q_i\) instead of \(p_i(b)\) and \(q_i(b)\).
\par Let \(I = \{i_1 < \cdots < i_r\} \subseteq \{1, ..., k\}\), and let \((\rho_i)_{i \in I}\) be any map \(I \to \mathbb{N}_{> 0}\) such that (1) \(\rho_i \leq \lambda_i\), (2) \(\rho_i\) is decreasing with \(i\), (3) \(\lambda_i - \rho_i\) is decreasing with \(i\), and (4) \(\rho_i < n\).
For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
Then, we define \(B_{I, (\rho_i)}\) as the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For all \(k \in \{0, ..., r\}\), \(p_{i_{k + 1}} = \max_{i : q_i < q_{i_k}} p_i\).
\end{itemize}
Let \(U_{I, (\rho_i)} = \{(A_{0, b}, U) \in V : b \in B_{I, (\rho_i)}\}\).

@@

\subsection{A study of \(B_{I, (\rho_i)}\)}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions (1)--(4).
Define \(\{i_1 < \cdots < i_r\} := I\).
Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).

\begin{lemma}\label{bs_fact}
    \begin{itemize}
        \item 
    \end{itemize}
\end{lemma}
To see why this choice makes some sort of sense, look at the shape \(\mu\) of the Jordan basis of the previous subsection.
\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\), where
    \[B_{I, (\rho_i)}' := \{b \in \mathbb{C}^m : \forall i \in I. \; p_i \leq \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
    \[\textrm{ where } k = \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\}.\]
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    So, let \(i \notin I\), and let \(k = \min\{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
